---
title: "Linear_Model"
author: "Judy Hua Zhu and Asreeta Ushasri"
date: "2025-04-06"
output: html_document
---
Introduction and Clarification:
We are creating three linear models with different independent variable combinations:
Model 1: Technology + Class
Model 2: Technology + Net Capacity Factor
Model 3: Technology + Annual Energy Generation

All work are done collectively as a team.

```{r message=FALSE, warning=FALSE}
#Load packages
library(tidyverse)
library(here)
library(dplyr)
library(readxl)
library(openxlsx)

#Load in data
Solar_ATB <- read.csv("Processed_Data/Solar_ATB_Long.csv")
```

```{r}
mean(Solar_ATB$LCOE)
sd(Solar_ATB$LCOE)
```

```{r}
Solar_ATB <- Solar_ATB %>%
  select(-"X")

Model1.lm <- lm(LCOE ~
                Technology +
                Class,
                data = Solar_ATB)
summary(Model1.lm)
plot(Model1.lm)

AIC(Model1.lm)

view(Solar_ATB)
```


```{r}
# Remove data point 
Solar_ATB_Model1.2 <- Solar_ATB[-c(125,137,142),]
Model1.2.lm <- lm(LCOE ~
                Technology +
                Class,
             data = Solar_ATB_Model1.2)
summary(Model1.2.lm)
plot_model1 <- plot(Model1.2.lm)
AIC(Model1.2.lm)

plot_model1 <- ggdraw() +
  draw_text("Assessing LCOE Multilevel Model Fit", 
            size = 16, fontface = "bold", x = 0.5, y = 0.97, hjust = 0.5) +
  draw_plot(plot_model1, y = 0.1, height = 0.8) +
  draw_text("The residuals appear mostly equally distributed, although there are slight vertical clusters in the residuals vs. fitted plot. The residuals follow the theoretical normal distribution in the QQ Plot, and in general show equal variance in scale-location plot. Therefore, we affirm that this meets the assumptions for a linear model.", 
            size = 10, x = 0.5, y = 0.4, hjust = 0.5)


```


```{r message=FALSE, warning=FALSE}
Model2.lm <- lm(LCOE ~
                Technology +
                Net_Capacity_Factor,
             data = Solar_ATB)
summary(Model2.lm)
plot(Model2.lm)
AIC(Model2.lm)


```

```{r}
# Remove data point 137,142,147
Solar_ATB_Model2.2 <- Solar_ATB[-c(137,142,147),]
Model2.2.lm <- lm(LCOE ~
                Technology +
                Net_Capacity_Factor,
             data = Solar_ATB_Model2.2)
summary(Model2.2.lm)
plot_model2 <- plot(Model2.2.lm)
AIC(Model2.2.lm)



assumptions <- ggdraw() +
  draw_text("Assessing LCOE Multilevel Model Fit", 
            size = 16, fontface = "bold", x = 0.5, y = 0.97, hjust = 0.5) +
  draw_plot(assumptions, y = 0.1, height = 0.8) +
  draw_text("The Fitted Values graph depicts equal variance amongst residuals
            in the multilevel model. The model meets requirements for homoscedasticity.
            The QQ Plot indicates the residuals follow the theoretical normal
            curve quite closely (except for a slight curve at the far right values).
            This model therefore meets the assumption for normally distributed residuals.", 
            size = 10, x = 0.5, y = 0.4, hjust = 0.5)

```

```{r}
# Model variable: Technology and generation
Model3.lm <- lm(LCOE ~
                Technology +
                log(Annual_Generation_MWh),
             data = Solar_ATB)
summary(Model3.lm)
plot(Model3.lm)
```
```{r}
# Remove data point 1,29,30
Solar_ATB_Model3.2 <- Solar_ATB[-c(95,110,125),]
Model3.2.lm <- lm(LCOE ~
                Technology +
                log(Annual_Generation_MWh),
             data = Solar_ATB_Model3.2)
summary(Model3.2.lm)
plot(Model3.2.lm)
AIC(Model3.2.lm)
```
As we can conclude Model 3 may be the best prediction for LCOE with highest adjusted R-squared value and lowest AIC value, although all three models have great predictions with significant p value (P<0.0001).

