---
title: "Evaluate variables"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(here)
library(readxl)
#install.packages("openxlsx")
library(openxlsx)
library(plyr)
getwd()
```


```{r}
Processed_ATB <- read_csv("Solar_ATB_Processed.csv")
```
```{r}
# Delete the first two columns 
Processed_ATB <- Processed_ATB[,-1]
Processed_ATB <- Processed_ATB[,-1]
# Factorize technology
Processed_ATB$Technology = factor (Processed_ATB$Technology, 
                levels = c("Advanced","Moderate","Conservative"))
Processed_ATB$Class = factor (Processed_ATB$Class, 
                levels = c(1,2,3,4,5,6,7,8,9,10))
```



```{r}
# Visualization
# Use Rice Rule(2n^(1/3)) to determine bin size
2*30^(1/3) #6.21, Bin size = 6

# Graph relationship of technology type to LCOE
ggplot(data = Processed_ATB, aes(x=Technology,y=LCOE,color=Technology))+
  geom_boxplot()+
  theme_bw()
# We can see Advanced technology has lowest LCOE, and conservative ones have higher LCOE
```
```{r}
# Graph relationship of Class type to LCOE
ggplot(data = Processed_ATB, aes(y=LCOE, x= Class,color=Class))+
  geom_boxplot()+
  #facet_wrap(~Class)+
  theme_bw()
```
```{r}
# Evaluate whether independent variables are normally distributed
ggplot(data = Processed_ATB, aes(Net_Cap_Factor))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Annual_Energy_Production))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(CAPEX))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Construct_Finance_Costs))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Overnight_Cap_Costs))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Fixed_OM))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Grid_Connect_Cost))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Variable_OM))+
  geom_histogram(bins=6)+
  theme_bw()
```
For initial visualization, we found out that CAPEX, Construction cost, Overnight capital cost, Fixed operation cost, and Grid connection cost only shows three values which fully depends on their technology type. Additionally, variable cost of solar panels is zero. Therefore, we decide not to proceed with all variables mentioned above, and only evaluate technology, class, capacity factor and generations influence on LCOE.

```{r}
# Graph relationship between capacity factor and LCOE
ggplot(data = Processed_ATB, aes(y=LCOE, x=Net_Cap_Factor,
                                 color=Technology))+
  geom_jitter()+
  labs(x= "Net Capacity Factor (%)",
       y = "LCOE ($/MWh)")+
  theme_bw()
# We can see that capacity factor is negatively related to LCOE. Conservative technology tends to cause higher LCOE.
```
```{r}
# Graph relationship between capacity factor and LCOE
ggplot(data = Processed_ATB, aes(y=LCOE, x=Annual_Energy_Production,
                                 color = Class))+
  geom_jitter()+
  labs(x= "Annual Energy Production (MWh)",
       y = "LCOE ($/MWh)")+ #Please check if it is MWh
  theme_bw()
# Annual Energy production is negatively related to LCOE. It is also interesting 
# to see that each class is stacked in three, with class 1 having highest production 
# and lowest LCOE, and class 10 on the opposite end.
```
```{r}
# Evaluate correlation between net capacity factor and annual energy production
# since they are the only two continuous variables.
cor.test(x=Processed_ATB$Net_Cap_Factor, y=Processed_ATB$Annual_Energy_Production)
# The results showed that capacity factor is correlated to annual energy production,
# therefore we need to place them in different models.
```
```{r}
# Final check: how capacity factor relates to annual energy production
ggplot(data = Processed_ATB, aes(y=Annual_Energy_Production, x=Net_Cap_Factor,
                                 color = Class))+
  geom_jitter()+
  theme_bw()
```

