---
title: "Evaluate variables"
output: html_document
---

```{r}
library(tidyverse)
library(plyr)
library(dplyr)
library(here)
library(readxl)
#install.packages("openxlsx")
library(openxlsx)
getwd()
```


```{r}
Processed_ATB <- read_csv("Solar_ATB_Processed.csv")

view(Processed_ATB)

```


```{r}
# Delete the first two columns 
Processed_ATB <- Processed_ATB[,-1]
view(Processed_ATB)

# Factorize technology
Processed_ATB$Technology = factor (Processed_ATB$Technology, 
                levels = c("Advanced","Moderate","Conservative"))
Processed_ATB$Class = factor (Processed_ATB$Class, 
                levels = c(1,2,3,4,5,6,7,8,9,10))
```



```{r}
# Visualization
# Use Rice Rule(2n^(1/3)) to determine bin size
2*30^(1/3) #6.21, Bin size = 6

# Graph relationship of technology type to LCOE
techplot <- ggplot(data = Processed_ATB, aes(x=Technology,y=LCOE,color=Technology))+
  geom_boxplot()+
  theme_bw() + 
  labs(title = "LCOE of Utility-Scale PV based on Technology Advancement,
       U.S. NREL Annual Technology Baseline (2022-2026)",
       caption =
"This graph examines the levelized cost of electricity and technology design level.
The National Renewable Energies Laboratory creates solar power projections based on
three categories of future potential technology directions. The advanced technology
category describes a future with high investment in solar research and development,
new efficient panels, and improved solar power performance. The moderate technology
category represents solar power outlook if the United States continued at the current
pace of panel design and development. The conservative categories indicates a future
in which solar panel research and development has slowed down, or efficiency remains
stagnant. As shown in the graph, the cost of producing one kWh of solar electricity
is lowest with the advanced technology future. The cost increases in the moderate
and conservation technology projections.") +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0)) 

techplot

ggsave(techplot,
       filename = "Tech_Plot.jpg",
       height = 15,
       width = 15,
       units = "cm")

# We can see Advanced technology has lowest LCOE, and conservative ones have higher LCOE

```
```{r}
# Graph relationship of Class type to LCOE
classplot <- ggplot(data = Processed_ATB, aes(y=LCOE, x= Class,color=Class))+
  geom_boxplot()+
  #facet_wrap(~Class)+
  theme_bw() + 
  labs(title = "LCOE of Utility-Scale PV based on Geographic Class,
       U.S. NREL Annual Technology Baseline (2022-2026)",
       caption =
"This graph examines the levelized cost of electricity and geographic class level.
The NREL has divided the U.S. into ten geographic categories based on the average
sunlight power per area (irridance) different regions receive. Class 1 receives 
the highest amount of solar power per area on average annually, while Class 10 counties
receive the lowest leve of solar power per area on average annually. As shown in
the graph, the cost of producing electricity increases as the class increases.") +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0)) 

classplot

ggsave(classplot,
       filename = "Class_Plot.jpg",
       height = 12,
       width = 15,
       units = "cm")


```

```{r}
# Evaluate whether independent variables are normally distributed
ggplot(data = Processed_ATB, aes(Net_Cap_Factor))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Annual_Energy_Production))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(CAPEX))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Construct_Finance_Costs))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Overnight_Cap_Costs))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Fixed_OM))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Grid_Connect_Cost))+
  geom_histogram(bins=6)+
  theme_bw()

ggplot(data = Processed_ATB, aes(Variable_OM))+
  geom_histogram(bins=6)+
  theme_bw()
```
For initial visualization, we found out that CAPEX, Construction cost, Overnight capital cost, Fixed operation cost, and Grid connection cost only shows three values which fully depends on their technology type. Additionally, variable cost of solar panels is zero. Therefore, we decide not to proceed with all variables mentioned above, and only evaluate technology, class, capacity factor and generations influence on LCOE.

```{r}
# Graph relationship between capacity factor and LCOE
cap_fac_plot <- ggplot(data = Processed_ATB, aes(y=LCOE, x=Net_Cap_Factor,
                                 color=Technology))+
  geom_jitter()+
  labs(x= "Net Capacity Factor (%)",
       y = "LCOE ($/MWh)")+
  theme_bw() +  
  labs(title = "LCOE of Utility-Scale PV based on Net Capacity Factor,
       U.S. NREL Annual Technology Baseline (2022-2026)",
       caption =
"This graph examines the levelized cost of electricity and net capacity factor.
As net capacity factor increases, the cost of producing each additional unit
of electricity (the LCOE) decreases. The technology categories are scattered,
though conservation technology predictions tend to have a higher LCOE.") +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0)) 

cap_fac_plot 

ggsave(cap_fac_plot ,
       filename = "Cap_Fac_Plot.jpg",
       height = 12,
       width = 15,
       units = "cm")
# We can see that capacity factor is negatively related to LCOE. Conservative technology tends to cause higher LCOE.
```
```{r}
# Graph relationship between capacity factor and LCOE
genplot1 <- ggplot(data = Processed_ATB, aes(y=LCOE, x=Annual_Energy_Production,
                                 color = Class)) +
  geom_jitter()+
  labs(x= "Annual Energy Production (MWh)",
       y = "LCOE ($/MWh)")+ #Please check if it is MWh
  theme_bw() +  
  labs(title = "LCOE of Utility-Scale PV based on Annual Energy Production,
       U.S. NREL Annual Technology Baseline (2022-2026)",
       caption =
"This graph examines the levelized cost of electricity and annual energy
production. As production increases, the cost of producing each additional unit
of electricity (the LCOE) decreases. Of interest, Class 1 observations have the
highest energy annual production and Class 10 observations have the lowest
annual energy generation.") +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0)) 

genplot1

ggsave(genplot1,
       filename = "Gen_Plot_Class.jpg",
       height = 12,
       width = 15,
       units = "cm")

# Annual Energy production is negatively related to LCOE. It is also interesting 
# to see that each class is stacked in three, with class 1 having highest production 
# and lowest LCOE, and class 10 on the opposite end.
```
```{r}
# Graph relationship between capacity factor and LCOE
genplot2 <- ggplot(data = Processed_ATB, aes(y=LCOE, x=Annual_Energy_Production,
                                 color = Technology)) +
  geom_jitter()+
  labs(x= "Annual Energy Production (MWh)",
       y = "LCOE ($/MWh)")+ #Please check if it is MWh
  theme_bw() +  
  labs(title = "LCOE of Utility-Scale PV based on Annual Energy Production,
       U.S. NREL Annual Technology Baseline (2022-2026)",
       caption =
"This graph examines the levelized cost of electricity and annual energy
production. As production increases, the cost of producing each additional unit
of electricity (the LCOE) decreases.") +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0)) 

genplot2

ggsave(genplot2,
       filename = "Gen_Plot_Tech.jpg",
       height = 12,
       width = 15,
       units = "cm")

# Annual Energy production is negatively related to LCOE. It is also interesting 
# to see that each class is stacked in three, with class 1 having highest production 
# and lowest LCOE, and class 10 on the opposite end.
```


```{r}
# Evaluate correlation between net capacity factor and annual energy production
# since they are the only two continuous variables.
cor.test(x=Processed_ATB$Net_Cap_Factor, y=Processed_ATB$Annual_Energy_Production)
# The results showed that capacity factor is correlated to annual energy production,
# therefore we need to place them in different models.
```
```{r}
# Final check: how capacity factor relates to annual energy production

#view(Processed_ATB)
class_cor_graph <- ggplot(data = Processed_ATB,
                          aes(y=Annual_Energy_Production,
                                                    x=Net_Cap_Factor, color = Class)) + geom_jitter() +
  theme_bw() +   
  labs(title = "Examining Correlation of Annual Energy Production
       and Net Capacity Factor",
       x = "Net Capacity Factor (%)",
       y = "Annual Energy Generation (MWh)",
       caption =
"This graph examines any correlation between annual energy production and net
capacity factor, identifying different geographic classes. As demonstrated
visually, annual energy production and net capacity factor has a strong, positive,
linear correlation. These two variables cannot be used as predictors in the same model.

Moreover, the categorical variable of class appears correlated to both annual
energy production and net capacity factor. Class 1, the regions with the highest
irradance (solar power per square meter) has both the highest energy production and
the highest net capacity. Similarly, Class 10 (regions with the lowest solar power
per square meter) has the lowest energy production and the lowest capacity factor.
Based on this visualization, geographic class should not be combined with annual
energy production or net capacity factor in a linear model when predicting LCOE.") +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0))
  class_cor_graph
  
  ggsave(class_cor_graph,
       filename = "class_cor_graph.jpg",
       height = 15,
       width = 15,
       units = "cm")
  
  
```
```{r}
# Correlation check between categorical variables and continuous variable
ggplot(data = Processed_ATB, aes(x=Technology,y=Net_Cap_Factor))+
  geom_boxplot()+
  theme_bw()

ggplot(data = Processed_ATB, aes(x=Technology,y=Annual_Energy_Production))+
  geom_boxplot()+
  theme_bw()

ggplot(data = Processed_ATB, aes(x=Class,y=Net_Cap_Factor))+
  geom_boxplot()+
  theme_bw()

ggplot(data = Processed_ATB, aes(x=Class,y=Annual_Energy_Production))+
  geom_boxplot()+
  theme_bw()
```

