---
title: "Data_Wrangling_2"
output: html_document

---
```{r message=FALSE, warning=FALSE}
#Set up
library(plyr)
library(dplyr)
library(tidyverse)
#install.packages("dplyr")
library(here)
library(readxl)
#install.packages("openxlsx")
library(openxlsx)
getwd()

```



```{r}
#Import ATB data
#Solar PV excel sheet has many tables of data
#Need to import data as separate data frames into R
#Specify cell range using read_xlsx function
#Make sure to install read_xl package

Solar_ATB <- read.csv("2024_ATB.csv")
#view(Solar_ATB)

#Rename columns

Solar_ATB <- Solar_ATB %>% 
  rename("Class" = `X.9`,
         "Technology" = `X.10`,
    "Year_2022" = `https...atb.nrel.gov.electricity.2024.utility.scale_pv`,
    "Year_2023" = `X.11`,
    "Year_2024" = `X.12`,
    "Year_2025" = `X.13`,
    "Year_2026" = `X.14`)

#view(Solar_ATB)

#Need to remove symbols, spaces, etc.

Solar_ATB$Class <- gsub("%", "", Solar_ATB$Class)
Solar_ATB$Class <- gsub(",", "", Solar_ATB$Class)
Solar_ATB$Class <- gsub("\\$", "", Solar_ATB$Class)
Solar_ATB$Class <- gsub(" ", "_", Solar_ATB$Class)
Solar_ATB$Class <- gsub("-", "_", Solar_ATB$Class)
Solar_ATB$Technology <- gsub("%", "", Solar_ATB$Technology)
Solar_ATB$Technology <- gsub(",", "", Solar_ATB$Technology)
Solar_ATB$Technology <- gsub("\\$", "", Solar_ATB$Technology)
Solar_ATB$Technology <- gsub(" ", "_", Solar_ATB$Technology)
Solar_ATB$Technology <- gsub("-", "_", Solar_ATB$Technology)
Solar_ATB$Year_2022 <- gsub("%", "", Solar_ATB$Year_2022)
Solar_ATB$Year_2022 <- gsub(",", "", Solar_ATB$Year_2022)
Solar_ATB$Year_2022 <- gsub("\\$", "", Solar_ATB$Year_2022)
Solar_ATB$Year_2023 <- gsub("%", "", Solar_ATB$Year_2023)
Solar_ATB$Year_2023 <- gsub(",", "", Solar_ATB$Year_2023)
Solar_ATB$Year_2023 <- gsub("\\$", "", Solar_ATB$Year_2023)
Solar_ATB$Year_2024 <- gsub("%", "", Solar_ATB$Year_2024)
Solar_ATB$Year_2024 <- gsub(",", "", Solar_ATB$Year_2024)
Solar_ATB$Year_2024 <- gsub("\\$", "", Solar_ATB$Year_2024)
Solar_ATB$Year_2025 <- gsub("%", "", Solar_ATB$Year_2025)
Solar_ATB$Year_2025 <- gsub(",", "", Solar_ATB$Year_2025)
Solar_ATB$Year_2025 <- gsub("\\$", "", Solar_ATB$Year_2025)
Solar_ATB$Year_2026 <- gsub("%", "", Solar_ATB$Year_2026)
Solar_ATB$Year_2026 <- gsub(",", "", Solar_ATB$Year_2026)
Solar_ATB$Year_2026 <- gsub("\\$", "", Solar_ATB$Year_2026)

#Create separate DF for each variable

Assumptions <- Solar_ATB[51:81, 10:17]
Net_Cap_Factor <- Solar_ATB[86:116, 10:17]
Annual_Energy_Production <- Solar_ATB[118:148, 10:17]
CAPEX <- Solar_ATB[150:180, 10:17]
Construct_Finance_Costs <- Solar_ATB[182:212, 10:17]
Overnight_Cap_Costs <- Solar_ATB[214:244, 10:17]
Fixed_OM <- Solar_ATB[246:276, 10:17]
Variable_OM <- Solar_ATB[278:308, 10:17]
Grid_Connect_Cost <- Solar_ATB[313:343, 10:17]
LCOE <- Solar_ATB[346:376, 10:17]
Tax_Credit <- Solar_ATB[378:381, 10:17]

#view(LCOE)
```


```{r}
#Create an average value for the five years

#Net Cap Factor
Net_Cap_Factor <- Net_Cap_Factor %>%
  mutate(Avg_Net_Cap = rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))


#Process annual energy production
Annual_Energy_Production <- Annual_Energy_Production %>%
  mutate(Avg_Annual_Energy_ =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#Next, process capex
CAPEX <- CAPEX %>%
  mutate(Avg_CAPEX =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#Processing CFC next
Construct_Finance_Costs <- Construct_Finance_Costs %>%
  mutate(Avg_Construct_Finance_Costs =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#Overnight Capacity Costs
Overnight_Cap_Costs <- Overnight_Cap_Costs %>%
  mutate(Avg_Overnight_Cap_Costs =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#FixedO&M
Fixed_OM <- Fixed_OM %>%
  mutate(Avg_Fixed_OM =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#VariableO&M
Variable_OM <- Variable_OM %>%
  mutate(Avg_Variable_OM =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#GridCC
Grid_Connect_Cost <- Grid_Connect_Cost %>%
  mutate(Avg_Grid_Connect_Cost =
           rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

#LCOE processing
LCOE <- LCOE %>%
  mutate(Avg_LCOE = rowMeans(select(., Year_2022:Year_2026) %>% 
                             mutate(across(everything(), as.numeric)),
                            na.rm = TRUE))

view(LCOE)


```


```{r}
#First, create a data frame for net capacity observations
#view(Grid_Connect_Costs)

dfs1 <- list(Net_Cap_Factor,
            Annual_Energy_Production,
            CAPEX,
            Construct_Finance_Costs,
            Overnight_Cap_Costs,
            Fixed_OM,
            Variable_OM,
            Grid_Connect_Cost,
            LCOE)

Solar_ATB_Net_Cap <- join(Net_Cap_Factor, LCOE, by = "Technology")

view(Solar_ATB_Net_Cap)

Solar_ATB_Net_Cap <- Solar_ATB_Net_Cap %>% 
  mutate(Class = factor(Class, levels = c("Utility_PV___Class_1",
                                          "Utility_PV___Class_2",
                                          "Utility_PV___Class_3",
                                          "Utility_PV___Class_4",
                                          "Utility_PV___Class_5",
                                          "Utility_PV___Class_6",
                                          "Utility_PV___Class_7",
                                          "Utility_PV___Class_8",
                                          "Utility_PV___Class_9",
                                          "Utility_PV___Class_10"),
                        labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)))


```

```{r}
#Next, make a data frame for annual energy production

dfs2 <- list(Annual_Energy_Production,
            Net_Cap_Factor,
            CAPEX,
            Construct_Finance_Costs,
            Overnight_Cap_Costs,
            Fixed_OM,
            Variable_OM,
            Grid_Connect_Cost,
            LCOE)

Solar_ATB_Annual_Gen <- join_all(dfs2,
                             by = c("Class", "Technology", "LCOE"),
                             type = "full")

Solar_ATB_Annual_Gen <- Solar_ATB_Annual_Gen %>% 
  mutate(Class = factor(Class, levels = c("Utility_PV___Class_1",
                                          "Utility_PV___Class_2",
                                          "Utility_PV___Class_3",
                                          "Utility_PV___Class_4",
                                          "Utility_PV___Class_5",
                                          "Utility_PV___Class_6",
                                          "Utility_PV___Class_7",
                                          "Utility_PV___Class_8",
                                          "Utility_PV___Class_9",
                                          "Utility_PV___Class_10"),
                        labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)))

view(Solar_ATB_Annual_Gen)

```


```{r}
#Remove the last row, blank/NA
Solar_ATB_Net_Cap <- Solar_ATB_Net_Cap[-31, -1]
Solar_ATB_Annual_Gen <- Solar_ATB_Annual_Gen[-31, -1]

#view(Solar_ATB_Processed)
getwd()

#Save processed data in new folder

write.csv(Solar_ATB_Annual_Gen, "C:/Users/Ashree/OneDrive/Desktop/Spring_2025/Stats_Modeling/ENV_710/Processed_Data/Net_Cap.csv")

write.csv(Solar_ATB_Annual_Gen, "C:/Users/Ashree/OneDrive/Desktop/Spring_2025/Stats_Modeling/ENV_710/Processed_Data/Annual_Gen.csv")
